---
title: "FML Assignment 3"
author: "Shivani Pitla"
date: "2022-10-16"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#installation of all the required packages
```{r}
library("class")
library("caret")
library("e1071")
library("dplyr")
library("ggplot2")
library("gmodels")
library("melt")
library("reshape")
library("reshape2")
library("readr")
library("ISLR")
library("pROC")
```

#importing the dataset
```{r}
universalbank <- read.csv("C:/Users/shiva/Downloads/UniversalBank (1).csv")
```



#normalizing and cleaning the data
```{r}
#Converting the predictor attributes to factors
universalbank$Personal.Loan <- as.factor(universalbank$Personal.Loan)
universalbank$Online <- as.factor(universalbank$Online)
universalbank$CreditCard <- as.factor(universalbank$CreditCard)
#checking for na values
test.na <- is.na.data.frame(universalbank)
#Data Partition
set.seed(310)
data_part <- createDataPartition(universalbank$Personal.Loan,p=.6, list=F)
Train <- universalbank[data_part,]
Validate <- universalbank[-data_part,]
#Data Normalization
normmodel_ub <- preProcess(Train[,-c(10,13:14)], 
                method=c("center","scale"))
Trainnorm_ub <- predict(normmodel_ub,Train)
Validatenorm_ub <- predict(normmodel_ub,Validate)
```


***A. Create a pivot table for the training data with Online as a column variable, CC as a row variable, and Loan as a secondary row variable***
```{r}
table1_ub<- ftable(Trainnorm_ub[,c(14,10,13)])
table1_ub
```


***B. The probability of the customers accepting loan who owns a bank credit card and is actively using online banking services = 51/(51+467) = 0.0984*** \vspace{3mm}\newline


***C. Creating two separate pivot tables for the training data. One having Loan (rows) as a function of Online (columns) and the other having Loan (rows) as a function of CC*** \vspace{3mm}\newline
```{r}
melt1_ub <- melt(Trainnorm_ub,id=c("Personal.Loan"),variable="Online")
melt2_ub <- melt(Trainnorm_ub,id=c("Personal.Loan"), variable="CreditCard")
castt1_ub <- dcast(melt1_ub, Personal.Loan~Online)
castt2_ub <- dcast(melt2_ub, Personal.Loan~CreditCard)
```

***D.Compute the following quantities [P(A | B) i.e. the probability of A given B]***
```{r}
ftable(Trainnorm_ub[,c(10,13)])
ftable(Trainnorm_ub[,c(10,14)])
ftable(Trainnorm_ub[,10])
```


*1. P(CC = 1 | Loan = 1) = 79/(79+209) =* ***0.2743***\vspace{3mm}\newline
*2. P(Online= 1 | Loan= 1) = 178/(178+110) =* ***0.6180***\vspace{3mm} \newline
*3. P(Loan = 1) = 288/(288+2712) =* ***0.096***\vspace{3mm} \newline
*4. P(CC= 1 | Loan= 0) = 806/(806+1906) =* ***0.2972***\vspace{3mm} \newline
*5. P(Online=1 |Loan=0) = 1598/(1598+1114) =* ***0.5892***\vspace{3mm} \newline
*6. P(Loan = 0) = 2712/(2712+288) =* ***0.904***\vspace{3mm} \newline


***E. Use the quantities computed above to compute the naive Bayes probability P(Loan = 1 | CC = 1, Online = 1)***

(0.2743 x 0.6180 x 0.096) / (0.2743 x 0.6180 x 0.096) + (0.2972 x 0.5892 x 0.904) = ***0.1000*** \vspace{3mm}\newline


***F. When we compare the value acquired in step b, which is 0.0984, to the value achieved in step a, which is 0.1000, we can see that both numbers are practically identical, although Naive Bayes has a slightly greater probability than that with the direct calculation.*** \vspace{3mm}\newline


***G. Run the Naive Bayes Model on the data***
```{r}
naive <- naiveBayes(Personal.Loan~Online+CreditCard,data=Trainnorm_ub)
naive
```
***When the Naive Bayes Model is run for the consumer taking the loan, using a credit card, and using online banking, the result is 0.1000, which is equivalent to the result in E.*** \vspace{3mm}\newline


*Using the validation data to predict the Naive Bayes model while also examining the AUC value and ROC curve*
```{r}
predlabels_ub <- predict(naive,Validatenorm_ub,type = "raw")
head(predlabels_ub)
roc(Validatenorm_ub$Online,predlabels_ub[,2])
plot.roc(Validatenorm_ub$Online,predlabels_ub[,2])
```